\section{Introduction}
\subsection{About \mntr}

\mntr{} is an open-source software toolkit for creating, modifying and solving
mixed integer nonlinear optimization problems (MINLPs). It provides libraries
for expressing MINLPs and also for commonly used tools for solving them.
 Using these libraries, a user can develop
new algorithms for general or application-specific MINLPs.  \mntr{} is under
active development. Please consider subscribing to the
\href{https://lists.mcs.anl.gov/mailman/listinfo/minotaur}{minotaur-users
email-list} for asking questions, proposing changes, reporting problems and
for updates about new developments.

\subsection{About This Manual}
This manual is intended to provide general guidelines for modifying existing
routines or adding new one. The precise description of individual files,
classes and functions in the source code are documented using Doxygen and are
available
\href{http://www.mcs.anl.gov/research/projects/minotaur/nightly/doxygen/}{online}.
This manual is intended to serve three purposes.
\begin{enumerate}
\item Present a general
overview of how basic components of \mntr{} interact with each other.
\item Provide documentation on how to use \mntr{} libraries for creating applications.
\item Give guidelines for modifying or adding routines to \mntr{} source-code
in order to enhance its capabilities.
\end{enumerate}

This manual is not intended to be a guide for using solvers that already come with
\mntr{}. Help for using these solvers is available on the
``\href{http://wiki.mcs.anl.gov/minotaur/index.php/Running\_Binaries}{Running
Binaries page of \mntr-wiki}'' or through the above mentioned
\href{https://lists.mcs.anl.gov/mailman/listinfo/minotaur}{minotaur-users
email-list}.
