%% Example of a Handler: QGHandler

\section{Customizing Minotaur}

There are two approaches of developing a custom solver for your specific
needs: (i) Use minotaur libraries, and (ii) modify minotaur libraries. Here we
will describe the later approach by modifying Minotaur to develop a
Quesada-Grossmann (QG) type solver for convex MINLPs. We can develop this
solver just by writing a Handler. We need to write a derived class of the base
class Handler. We do not need to write those functions that are not relevant
to QG.

\begin{enumerate}
\item \code+std::string getName()+: This function must return a string
containing the name of the handler. It is used for for
debugging and displaying status only. We just return the string ``QG Handler''
here.
\item \code+relax(RelaxationPtr rel, Bool isInf, BoolVector &c_list)+ 
\begin{enumerate}
\item Copy linear constraints from problem to relaxation. 
\item Make a list of nonlinear constraints in problem.
\item Solve NLP relaxation of problem.
\item Obtain linearization of non-linear constraints at the NLP solution. Add
those linearizations to relaxation.
\end{enumerate}
\item \code+Bool isFeasible(const Double *x, RelaxationPtr relaxation,+
\code+ Bool & isInfeasible)+ 
\begin{enumerate}
\item Check, using VariableHandler, if \code+x+ satisfies integrality 
constraints.
\item If not integer, return \code+false+.
\item Otherwise, check if \code+x+ satisfies all nonlinear constraints.
\item If satisfied, \code+return true+.
\end{enumerate}
\item \code+void separate(const Double *x, NodePtr node,+\\
\code+ RelaxationPtr rel, SolutionPoolPtr s_pool,+\\
\code+ Bool *sol_found,+ \code+ SeparationStatus *status)+
\begin{enumerate}
\item Solve NLP by fixing all integer variables to values in \code+x+. 
\item If we get an optimal solution that is better than the best ub, update
ub. Additionally, if the optimal solution value is same as that of node LP
relaxation, set status to \code+SepaPrune+.
\item Add to relaxation, linearizations about the the optimal solution or the
point where NLP engine converged. Set status to \code+SepaResolve+.
\end{enumerate}
\end{enumerate}

The functions:
\code+getBranchingCandidates()+, \code+getBrMod()+, \code+getBranches()+, 
\ldots are not relevant to Q-G and hence they are not required.

